DeepSphere: a graph-based spherical CNN

### 2019-09-11 main.tex
add size and optimal in climate exp

\begin{tabular}{l|c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
        \cmidrule(lr){2-5}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67\\
        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5\\
        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5
        % 590k
        % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

* DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m
        % 590k
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

>>>>

\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67 & 330k\\
        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
        % 590k
        DS-optimal (non-weighted) & 99.8 & 73.4 & 92.7 & 88.7 & \\ \hline
        %DS-Cohen (weighted) &
        % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

* DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\
* DS-optimal has 2 times the number of feature maps of DS.\\

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
        % 590k
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 55 & 22h \\
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}
